When Do You Repeat Yourself?\\ Voices from the Trenches of Linux Kernel Maintainers on Code Duplication

### 2025-11-01 papers/techdebt2026/techdebt.tex
techdebt2026: techdebt: update Zenodo URL for replication package
Given that we had to update the package on Zenodo due to the author's
name being present, update the Zenodo URL.

Signed-off-by: David Tadokoro <davidbtadokoro@usp.br>

Given the duplicated function pair, we observed that the files in the functions contained multiple other duplications. Thus, we proposed a simple systematic approach to mitigate all the functions duplicated in the context, not just the duplicated function pairs. After approaching the duplications with a systematic strategy, we sent a patch to the AMD development mailing list for the feedback of maintainers, while documenting the process, interactions, and impressions (available in our replication package\footnote{\url{https://doi.org/10.5281/zenodo.17474124}}).

@@

All anonymized threads containing the entire review process and interactions with maintainers are available in this Zenodo repository: \href{https://doi.org/10.5281/zenodo.17474124}{https://doi.org/10.5281/zenodo.17474124}.

>>>>

Given the duplicated function pair, we observed that the files in the functions contained multiple other duplications. Thus, we proposed a simple systematic approach to mitigate all the functions duplicated in the context, not just the duplicated function pairs. After approaching the duplications with a systematic strategy, we sent a patch to the AMD development mailing list for the feedback of maintainers, while documenting the process, interactions, and impressions (available in our replication package\footnote{\url{https://doi.org/10.5281/zenodo.17503684}}).

@@

All anonymized threads containing the entire review process and interactions with maintainers are available in this Zenodo repository: \href{https://doi.org/10.5281/zenodo.17503684}{https://doi.org/10.5281/zenodo.17503684}.
